Papers

### 2024-10-27 papers.qmd
update

- Karadzhov, G., Vlachos, A., & Stafford, T. (2024). The effect of diversity on group decision-making. arXiv preprint [arXiv:2402.01427](https://arxiv.org/abs/2402.01427).

@@

@@

-   Farag, Y., Brand, C. O., Amidei, J., Piwek, P., Stafford, T., Stoyanchev, S., & Vlachos, A. (2023). Opening up Minds with Argumentative Dialogues. SiCON 2023 (co-located with ACL 2023) [[preprint]](https://arxiv.org/abs/2301.06400)

@@

-   Holroyd, J., Scaife, R., Stafford, T. (in press). [What is implicit bias](http://onlinelibrary.wiley.com/doi/10.1111/phc3.12437/full)? Philosophy Compass, 12(10), e12437.

-   Holroyd, J., Scaife, R., Stafford, T. (in press). [Responsibility for Implicit Bias](http://onlinelibrary.wiley.com/doi/10.1111/phc3.12410/abstract). Philosophy Compass, 12(3), e12410.

@@

>>>>

- Zhu, X., Zhang, C., Stafford, T., Collier, N., & Vlachos, A. (2024). Conformity in Large Language Models. arXiv preprint [arXiv::2410.12428](https://doi.org/10.48550/arXiv.2410.12428)

@@

- Karadzhov, G. M., Vlachos, A., & Stafford, T. (2024). The effect of diversity on group decision-making. Proceedings of the Annual Meeting of the Cognitive Science Society, 46(0). https://escholarship.org/uc/item/6685n22z. arXiv preprint [arXiv:2402.01427](https://arxiv.org/abs/2402.01427).

@@

-   Farag, Y., Brand, C., Amidei, J., Piwek, P., Stafford, T., Stoyanchev, S., & Vlachos, A. (2022). Opening up Minds with Argumentative Dialogues. In Y. Goldberg, Z. Kozareva, & Y. Zhang (Eds.), Findings of the Association for Computational Linguistics: EMNLP 2022 (pp. 4569–4582). Association for Computational Linguistics. https://doi.org/10.18653/v1/2022.findings-emnlp.335

@@

@@

-   Holroyd, J., Scaife, R., Stafford, T. (2017). [What is implicit bias](http://onlinelibrary.wiley.com/doi/10.1111/phc3.12437/full)? Philosophy Compass, 12(10), e12437.

-   Holroyd, J., Scaife, R., Stafford, T. (2017). [Responsibility for Implicit Bias](http://onlinelibrary.wiley.com/doi/10.1111/phc3.12410/abstract). Philosophy Compass, 12(3), e12410.
